Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-18 Docs/TODAES/paper.tex
minor changes
SBESC reviewer's suggestions done + new vZ times

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

% Page heads
\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}

@@

\begin{abstract}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing. In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores. Each instance checks for a different optimum value until the optimization problem is satisfied. We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and also integrate the maximum satisfiability solver $\nu$Z tool into ESBMC. We compare all our approaches to another state-of-the-art optimization tool (Matlab). Experimental results show that there is no single optimization tool to solve all HW-SW partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve HW-SW partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
\end{abstract}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times in GA (average taken) and just once in ESBMC, $\nu$Z, and ILP. The reason is that GA times are not so close as ESBMC, $\nu$Z, and ILP. A time out condition (TO) is reached when the verification time is longer than $7200$ seconds. A memory out (MO) occurs when the tool reaches $24$GB of memory.

@@

%vZ
\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
&  T(s)   &  0.2   &  0.3   &  0.6   &  109   &  112    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  241    &  -   &  -  \\

>>>>

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}

\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

% Page heads
\markboth{A. Trindade et al.}{Multi-Core Model Checking and Maximum Satisfiability Applied to HW/SW Partitioning}

@@

\begin{abstract}
We present an alternative approach to solve the hardware and software partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open Multi-Processing. In a nutshell, the multi-core SMT-based BMC approach allows initializing many verification instances based on the number of available processing cores. Each instance checks for a different optimum value until the optimization problem is satisfied. We implement our algorithms on top of the Efficient SMT-Based Context-Bounded Model Checker (ESBMC) and also integrate the maximum satisfiability solver $\nu$Z tool into ESBMC. We compare all our approaches to another state-of-the-art optimization tool (Matlab). Experimental results show that there is no single optimization tool to solve all hardware-software partitioning benchmarks; however, Matlab and ESBMC-$\nu$Z are the most efficient ones to solve hardware-software partitioning problems, although multi-core ESBMC had a significant performance improvement in particular cases.
\end{abstract}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP. A time out condition (TO) is reached when the verification time is longer than $7200$ seconds. A memory out (MO) occurs when the tool reaches $24$GB of memory.

@@

%vZ
\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
&  T(s)   &  0.3   &  0.3   &  0.7   &  86.4   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
